Music Classification Using Convolutional Neural Networks

### 2019-12-15 docs/paper.tex
add our approach to docs

\subsection{Our Goals}

@@

>>>>

\subsection{Our Goal}

@@

\section{Our Approach}

There are many existing solutions and research papers regarding the subject and these 
show absolutely usable methods and results, though each of them tend to have a major 
drawback: every solution aims to work in \emph{centralized environments} due to their 
computational requirements. We decided that our approach had to be able to work on 
edge devices such as smart phones or other, more constrained environments, even on 
cost of precision. This decision implied a rather small model size and great model 
simplicity, this is why we chose to try a simple convolutional neural network.
